---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# sagemaker-tidymodels

`sagemaker-tidymodels` is an [AWS Sagemaker](https://aws.amazon.com/sagemaker/)
framework for training and deploy machine learning models written in R. 

This framework lets you use the same [tidymodels](https://www.tidymodels.org/)
script in development to cloud-based training and deployment.  

## Installation

This Python package is not yet available on PyPi. In the meantime, you can
install it from Github:
```bash
https://github.com/tmastny/sagemaker-tidymodels.git
pip install sagemaker-tidymodels/
```

The docker image is hosted on [dockerhub](https://hub.docker.com/repository/docker/tmastny/sagemaker-tidymodels),
or you can pull directly with 
```bash
docker pull tmastny/sagemaker-tidymodels
```

## Usage

The `sagemaker-tidymodels` Python package provides simple wrappers around
the [Estimator](https://sagemaker.readthedocs.io/en/stable/api/training/estimators.html)
and  Model `sagemaker` classes. 

The main difference is the `entry_point` parameter, where you can supply
an R script. This R script should encompass your end-to-end training.

```{python, eval=FALSE}
from sagemaker_tidymodels import Tidymodels

tidymodels = Tidymodels(
    entry_point="train.R",
    train_instance_type="local",
    role=role,
    image_name="sagemaker-tidymodels",
)

s3_data <- "s3://sagemaker-sample-data-us-east-2/processing/census/census-income.csv"
tidymodels.fit({'train': s3_data})
```

`train.R` is a normal R script, with a few necessary additions so it can
run on the command line effectively. 

```{r, eval=FALSE, code=readLines("tests/basic-train.R")}
```

1. The first line should be the shebang `#!/usr/bin/env Rscript`, so it can be
   ran as `./train.R` as required by the framework.
   
2. All the training logic should be wrapped by the following `if` statement. 
   This seems a little mysterious, but it makes sure that the training logic
   doesn't accidentally run when we've deployed our model for predictions. 
   See advanced usage below for more details.
```r
if (sys.nframe() == 0) {
  # training logic goes here!
}
```

3. Sagemaker is very specific about input and output locations. The input
   data path is found in an environment variable that can be read using
   `Sys.getenv('SM_CHANNEL_TRAIN')`. Likewise, the output model path can
   be found with `Sys.getenv('SM_MODEL_DIR')`.
